Component-Based Framework of Lightweight Ruby for Efficient Embedded Software Development

### 2016-10-25 jssst/paper.tex
Add results of research

\begin{table*}[t]
    \caption{Comparison of proposed and previous methods}
    \label{tab:comparison}
    \begin{center}
    {\tabcolsep=0.05cm
    \begin{tabular}{c||c|cccccc}
        & \shortstack{Bluetooth\\Loader}
        & \shortstack{Call\\C Function} 
        & \shortstack{Legacy Code of\\Embedded System} 
        & \shortstack{VM\\Management} 
        & \shortstack{VM\\Scheduler} 
        & \shortstack{Synchronization\\of Applications} \\ \hline
        python-on-a-chip \cite{url:python-on-a-chip} &            &            &            &            &             &            \\
        Owl system \cite{par:owl}                    &            & \checkmark & Partially  &            &             &            \\
        eLua \cite{url:eLua}                         &            & \checkmark & Partially  &            &             &            \\
        ChaiScript \cite{url:ChaiScript}             &            &            &            &            &             &            \\
        Squirrel \cite{url:Squirrel}                 &            & \checkmark &            &            &             &            \\
        mruby \cite{par:mruby}                       &            & \checkmark &            &            &             &            \\
        mruby on TECS \cite{par:mrubyonTECS}         &            & \checkmark & \checkmark & \checkmark &             &            \\
        Proposed framework                           & \checkmark & \checkmark & \checkmark & \checkmark & \checkmark  & \checkmark \\
    \end{tabular}
    }
    \end{center}
\end{table*}

@@

\section{Results of Research}
\label{sec:Results}
The proposed framework on LEGO MINDSTORMS EV3 \cite{url:download} has been certified for the official platform of ET Robocon 2016\footnote{http://www.etrobo.jp/2016/}.

>>>>

\begin{table*}[t]
    \caption{Comparison of proposed and previous methods}
    \label{tab:comparison}
    \begin{center}
    {\tabcolsep=0.05cm
    \begin{tabular}{c||c|cccccc}
        & \shortstack{Bluetooth\\Loader}
        & \shortstack{Call\\C Function} 
        & \shortstack{Legacy Code of\\Embedded System} 
        & \shortstack{VM\\Management} 
        & \shortstack{VM\\Scheduler} 
        & \shortstack{Synchronization\\of Applications} \\ \hline
        python-on-a-chip \cite{url:python-on-a-chip} &            &            &            &            &             &            \\
        Owl system \cite{par:owl}                    &            & \checkmark & Partially  &            &             &            \\
        eLua \cite{url:eLua}                         &            & \checkmark & Partially  &            &             &            \\
        ChaiScript \cite{url:ChaiScript}             &            &            &            &    -       &    -        &            \\
        Squirrel \cite{url:Squirrel}                 &            & \checkmark &            &            &             &            \\
        mruby \cite{par:mruby}                       &            & \checkmark &            &            &             &            \\
        mruby on TECS \cite{par:mrubyonTECS}         &            & \checkmark & \checkmark & \checkmark &             &            \\
        Proposed framework                           & \checkmark & \checkmark & \checkmark & \checkmark & \checkmark  & \checkmark \\
    \end{tabular}
    }
    \end{center}
\end{table*}

@@

\section{Results of Research}
\label{sec:Results}
The proposed framework on LEGO MINDSTORMS EV3 \cite{url:download} has been certified for the official platform of ET Robocon 2016\footnote{http://www.etrobo.jp/2016/ (in Japanese)}.
In ET Robocon 2016, the team with the proposed framework took second place at a regional competition.
